Inferring Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-07-02 doc/paper-lcr.tex
re-wrote theory

Strong lenses sit in our real Universe -- they are not truely isolated;
there is some mass along the line of sight coming from intervening structures.
These structures may be physically associated with the lens e.g. other members
of a group or cluster, or they may be the result of chance alignments at any redshift. 
Whilst it is rare for three galaxies to line up well enough for both of the background sources
to be strongly lensed \citep{gavazzi2008,collett2012}, the shear scale of dark matter halos
makes a partial allignment -- with the additional structure acting as a weak lens -- 
a near certainty, indeed \citet{valewhite2003} and \citet{hilbert2007} find that there
are no empty lightcones in a realistic universe. These additional structures induce an external shear
which can be recovered in the mass-modelling of the lens, but they can also introduce a convergence that
is undetectable from the image positions, shapes and relative fluxes; {\it the mass sheet-degeneracy} \citep[see e.g.][for details]{Falco1985,Schneider2006}. Similar to Eq. \ref{eq:psikappa} the convergence from an isolated mass sheet is by the ratio of the projected surface mass density devided by the critical density at the redshift of the mass sheet.
\flag{but is this the kappa that enters the lens modelling?}
In the case of several mass sheets at redshifts $\{z_{\mathrm{p}}\}$, with surface mass densities $\{\Sigma_{\mathrm{p}}\}$, the effective convergence is given by the \flag{weighted?} sum :
\be \label{eq:kappasum}
\kappax=\frac{4\pi G}{c^2}\sum_{\mathrm{p}}\frac{\Sigma_{\mathrm{p}}D_{\mathrm{p}} D_{{\rm ps}}}{D_{\rm s}}.
\ee

@@

In this work our aim is to quantify the lensing contribution from mass sheets that
are not physically associated with the lens galaxy -- mass-sheets lying infront or behind
the lens. We also aim to quantify how uncertainties in the estimations of kappa
propogate into uncertainties on the cosmological parametres which can be inferred
from measurements of $\Dt$.

>>>>

Strong lenses sit in our real Universe -- they are not truely isolated;
there is some mass along the line of sight coming from intervening structures.
These structures may be physically associated with the lens e.g. other members
of a group or cluster, or they may be the result of chance alignments at any redshift. 
Whilst it is rare for three galaxies to line up well enough for both of the background sources
to be strongly lensed \citep{gavazzi2008,collett2012}, the shear scale of dark matter halos
makes a partial allignment -- with the additional structure acting as a weak lens -- 
a near certainty, indeed \citet{valewhite2003} and \citet{hilbert2007} find that there
are no empty lightcones in a realistic universe. These additional structures induce an external shear
which can be recovered in the mass-modelling of the lens, but they can also introduce a convergence that
is undetectable from the image positions, shapes and relative fluxes; {\it the mass sheet-degeneracy} \citep[see e.g.][for details]{Falco1985,Schneider2006}. Similar to Eq. \ref{eq:psikappa} the convergence from an isolated mass sheet is by the ratio of the projected surface mass density devided by the critical density at the redshift of the mass sheet.
\flag{but is this the kappa that enters the lens modelling?}
In the case of several mass sheets at redshifts $\{z_{\mathrm{p}}\}$, with surface mass densities $\{\Sigma_{\mathrm{p}}\}$, the effective convergence is given by the \flag{weighted?} sum:
\be \label{eq:kappasum}
\kappax=\frac{4\pi G}{c^2}\sum_{\mathrm{p}}\frac{\Sigma_{\mathrm{p}}D_{\mathrm{p}} D_{{\rm ps}}}{D_{\rm s}}.
\ee

@@

In this work our aim is to quantify the lensing effect of mass-sheets that are physically associated with the lens galaxy -- mass-sheets
lying infront or behind the lens -- and the uncertainties induced by reconstructing
those mass-sheets using simple prescriptions applied to potential astronomical observables.
We also aim to quantify how uncertainties in the
estimations of $\kappax$ propogate into uncertainties on the cosmological parametres
which can be inferred from measurements of $\Dt$.
